paper_replication

### 2021-12-11 paper_replication.Rmd
Update paper_replication.Rmd

---
title: "paper_replication"
output: pdf_document
---
TODO: classify counties as highly restrictive or not
    - option 1: we can use the summary data that Alice linked to
    (https://www.guttmacher.org/article/2019/08/state-abortion-policy-landscape-hostile-supportive)
    - option 2: dig through the detailed legislation data and use the 3/4 types classification they did in the paper (http://lawatlas.org/datasets/abortion-laws)
    I'd say let's start with the summary data, and we do the extra work to make a more faithful replication later if we have time at the end.

@@

>>>>

---
title: "paper_replication"
output: pdf_document
---

BIG PROBLEM: data on abortion restrictions starts at the end of December 2018, but data on abortion counts only goes up to (max) 2018
   * Option 1: Somehow find abortion restriction data from before December 2018 - I tried with no luck yet
   * Option 2: Somehow find abortion count data for 2019 on - Also tried with no luck yet 
         - I found this by state but not by county.

TODO: classify counties as highly restrictive or not
    - option 1: we can use the summary data that Alice linked to
    (https://www.guttmacher.org/article/2019/08/state-abortion-policy-landscape-hostile-supportive)
    - option 2: dig through the detailed legislation data and use the 3/4 types classification they did in the paper (http://lawatlas.org/datasets/abortion-laws)
    I'd say let's start with the summary data, and we do the extra work to make a more faithful replication later if we have time at the end.

@@

TODO: Calculate abortion rates by county
